``Interestingness'' in Mathematical Theory Exploration

### 2018-05-17 PhDThesis/related_formalstats.tex
More dedupe

\paragraph{Structured Data}

The task of dimension reduction changes when we consider \emph{structured}
data. Recursive structures, like trees and lists, have \emph{fractal} dimension:
adding layers to a recursive structure gives us more \emph{fine-grained}
features, rather than \emph{orthogonal} features. For data mining context-free
languages (e.g. those of programming and theorem-proving systems), we will
mainly be concerned with tree structures of variable size.

Any investigation of variable-size input would be incomplete without mentioning
\emph{sequencing}. This is a lossless approach, which splits the input into
fixed-size \emph{chunks}, which are fed into an appropriate ML algorithm one at
a time. The sequence is terminated by a sentinel; an ``end-of-sequence'' marker
which, by construction, is distinguishable from the data chunks. This technique
allows us to trade \emph{space} (the size of our input) for \emph{time} (the
number of chunks in a sequence).

@@

>>>>

\paragraph{Sequences}

To handle input of \emph{variable} size, most attention has been given to the
handling of \emph{sequences}. This is a lossless approach, which splits the
input into fixed-size \emph{chunks}, which are fed into an appropriate ML
algorithm one at a time. The sequence is terminated by a sentinel; an
``end-of-sequence'' marker which, by construction, is distinguishable from the
data chunks. This technique allows us to trade \emph{space} (the size of our
input) for \emph{time} (the number of chunks in a sequence).

@@

\paragraph{Recursive Structure}

Recursive structures, like trees and lists, have \emph{fractal} dimension:
adding layers to a recursive structure gives us more \emph{fine-grained}
features, rather than \emph{orthogonal} features. For data mining context-free
languages (e.g. those of programming and theorem-proving systems), we will
mainly be concerned with tree and graph structures of variable size.
